
# Libraries
```{r, message = F}
library(tidyverse)

.libPaths(
  c('H:/DaSH416/R_libraries/R_Transfer_25062020',
    'H:/DaSH416/R_libraries/R_Libraries_15072020',
    'H:/DaSH416/R_libraries/R_Transfer_06012021'))

library(here)
library(vroom)
library(lubridate)
library(janitor)
library(comorbidity)

options(scipen = 999)
```

# Load original shielding data
```{r message = F}
#tidy and combine "pregnant" with "other" group
shielding_long <-
  vroom(here("original_data", 'Dash416_Shield20201012_Release.csv'),
        delim = "¬") %>%
  clean_names() %>%
  rename(id = dash416_release_uid) %>%
  mutate(date_addition = as_date(ymd_hms(earliest_addition_this_chi)),
         date_death = as_date(ymd(trak_person_deceased_date))) %>%
  select(id,
         group,
         origin_for_this_group,
         date_addition,
         removal_description,
         date_death) %>%
  mutate(group = ifelse(group == 6, 7, group)) %>%
  distinct()

#add translation of shielding group codes
shielding_long <-
  vroom(here("original_data", "shielding_codes_short.csv"),
        delim = ",") %>%
  left_join(shielding_long, ., by = c("group" = "shielding_group"))

demog <-
  vroom(here("original_data", 'Dash416_Shield20201012_Demographic_Release.csv'),
        delim = "¬") %>%
  rename(id = Dash416_Release_UID) %>%
  clean_names() %>%
  select(id, calc_sex, calc_dob)

vulnerability <-
  vroom(here("original_data", 'Dash416_Shield20201012_vulnerability_Release.csv'),
        delim = "¬") %>%
  clean_names() %>%
  rename(id = dash416_release_uid,
         simd_quintile = simd2020v2_quintile, 
         ur_name = u_rname) %>%
  select(id, simd_quintile, ur_name)
```


# Population exclusions
```{r}
#anyone not on shielding list before 1 Aug
#anyone who died before 28 March
#false positives
#moved from Scotland
shielding_long <-
  shielding_long %>%
  filter(date_addition <= ymd("2020-07-31")) %>%
  filter(date_death > ymd("2020-03-28") |
           is.na(date_death)) %>%
  filter(
    !removal_description %in%
      c("FalsePosLungCancer", "False Positive", "Moved out of Scotland")) 

unique_ids <- unique(shielding_long$id)
```


# Tidy demographic data
```{r}
demog <- 
  demog %>%
    filter(id %in% unique_ids)

#create variables for sex and age band
demog <- demog %>%
  mutate(
    sex = if_else(calc_sex == 1, "F", "M"),
    dob = ymd(calc_dob),
    age = as.period(interval(dob, ymd("2020-03-01")), units = "years")$year,
    age_band = 
      case_when(
        age %in% c(0:29) ~ "0-29",
        age %in% c(30:49) ~"30-49",
        age %in% c(50:69) ~"50-69",
        age %in% c(70:120) ~"70+")) %>%
  select(-calc_sex, -calc_dob)

demog$age_band <- factor(demog$age_band, levels = c("0-29", "30-49", "50-69", "70+"))

#add details of shielding reasons to demographics
demog <- 
  demog %>%
  left_join(., vulnerability, by = "id")

#add some demographics values to long shielding list
shielding_long <-
  demog %>%
    select(id, age, age_band, sex, simd_quintile, ur_name) %>%
  left_join(shielding_long, ., by = "id") 

rm(vulnerability)
```

# Tidy hospital admissions
```{r}
#load data, rename variables, format dates, select only variables needed
smr01 <-
  vroom(here("original_data", 'Dash416_Shield20201012_SMR01_Release.csv'),
        delim = "¬") %>%
  clean_names() %>%
  rename(
    id = dash416_release_uid,
    main_condition = main_cod,
    other_condition1 = oc1,
    other_condition2 = oc2,
    other_condition3 = oc3,
    other_condition4 = oc4,
    other_condition5 = oc5
  ) %>%
  mutate(
    date_episode_start = as_date(ymd(date_episode_start)),
    date_episode_end = as_date(ymd(date_episode_end)),
    date_admission = as_date(ymd(adm_date)),
    date_discharge = as_date(ymd(date_discharge)),
    episode_id = paste(id, date_episode_start, sep = "_")) %>%
  unite(
    diagnoses_admission, 
    c(main_condition:other_condition5), 
    remove = F, sep = ", ", na.rm = T) %>%
  select(
    id,
    episode_id,
    date_episode_start,
    date_admission,
    date_discharge,
    date_episode_end,
    main_condition,
    other_condition1,
    other_condition2,
    other_condition3,
    other_condition4,
    other_condition5,
    diagnoses_admission
  )
```

#Date exclusions
```{r}
#select date range and those in NDL population
smr01 <- 
  filter(smr01, 
         date_episode_start >= ymd("2018-03-01"),
         date_episode_end <= ymd("2020-02-29"),
         id %in% unique_ids)
```


#Calculate morbidity for admissions
```{r}
#get main condition diagnosed for last phase of spell
main_condition_last_admission <-
smr01 %>%
  group_by(episode_id) %>%
  arrange(date_admission) %>%
  slice_tail() %>%
  ungroup() %>%
  select(episode_id, id, date_episode_start, main_condition) 

#use R package comorbidity to calculate to NDL specs
admission_morbidity <-
  comorbidity(
    x = main_condition_last_admission,
    id = "episode_id",
    code = "main_condition",
    score = "elixhauser",
    icd = "icd10",
    assign0 = T
  ) %>%
  separate(episode_id, into = c("id", "date"), sep = "_")
```

#Calculate morbidity for people
```{r}
#make longer df that has one diagnosis per row (comorbidity input)
smr01_diagnoses <-
smr01 %>%
  pivot_longer(main_condition:other_condition5, values_drop_na = T) %>%
  select(id, episode_id, date_episode_start, name, value) 

#use R package comorbidity to calculate to NDL specs
person_morbidity <-
  comorbidity(
    x = smr01_diagnoses,
    id = "id",
    code = "value",
    score = "elixhauser",
    icd = "icd10",
    assign0 = T
  ) %>%
  mutate(score_band = case_when(score == 0 ~ 0,
                                score == 1 ~ 1,
                                score > 1 ~ 2))
```

#Tables 2.2 and 2.3
```{r}
demog_morbidity <-
demog %>%
  left_join(., person_morbidity, by = "id") 

demog_morbidity %>%
  group_by(score_band) %>%
  summarise(n_people = n()) %>%
  adorn_totals() %>%
  write_csv(., "table_2.2_overall.csv")

demog_morbidity %>%
  group_by(windex_vw) %>%
  summarise(n_people = n()) %>%
  adorn_totals() %>%
  write_csv(., "table_2.3_overall.csv")

demog_morbidity %>%
group_by(sex, score_band) %>%
  summarise(n_people = n()) %>%
  adorn_totals() %>%
  write_csv(., "table_2.2_sex.csv")

demog_morbidity %>%
  group_by(sex, windex_vw) %>%
  summarise(n_people = n()) %>%
  adorn_totals() %>%
  write_csv(., "table_2.3_sex.csv")

demog_morbidity %>%
group_by(age_band, score_band) %>%
  summarise(n_people = n()) %>%
  adorn_totals() %>%
  write_csv(., "table_2.2_age.csv")

demog_morbidity %>%
  group_by(age_band, windex_vw) %>%
  summarise(n_people = n()) %>%
  adorn_totals() %>%
  write_csv(., "table_2.3_age.csv")

demog_morbidity %>%
group_by(simd_quintile, score_band) %>%
  summarise(n_people = n()) %>%
  adorn_totals() %>%
  write_csv(., "table_2.2_deprivation.csv")

demog_morbidity %>%
  group_by(simd_quintile, windex_vw) %>%
  summarise(n_people = n()) %>%
  adorn_totals() %>%
  write_csv(., "table_2.3_deprivation.csv")
```

#Tables Reasons
```{r}
#nb people can have more than one reason for shielding

shielding_long_morbidity <-
shielding_long %>%
  left_join(., person_morbidity, by = "id")

shielding_long_morbidity %>%
  group_by(shielding_group_description, score_band) %>%
  summarise(n_people = n()) %>%
  adorn_totals() %>%
  write_csv(., "table_2.2_reasons.csv")

shielding_long_morbidity %>%
  group_by(shielding_group_description, windex_vw) %>%
  summarise(n_people = n()) %>%
  adorn_totals() %>%
  write_csv(., "table_2.3_reasons.csv")
```

#Tables Conditions
```{r}
summary_admissions <-
admission_morbidity %>%
  summarise(
    n_people = n_distinct(id),
    n_diagnoses = n(),
    chf = sum(chf == 1),
    carit = sum(carit == 1),
    valv = sum(valv == 1),
    pcd = sum(pcd == 1),
    pvd = sum(pvd == 1),
    hypunc = sum(hypunc == 1),
    hypc = sum(hypc == 1),
    para = sum(para == 1),
    ond = sum(ond == 1),
    cpd = sum(cpd == 1),
    diabunc = sum(diabunc == 1),
    diabc = sum(diabc == 1),
    hypothy = sum(hypothy == 1),
    rf = sum(rf == 1),
    ld = sum(ld == 1),
    pud = sum(pud == 1),
    lymph = sum(lymph == 1),
    metacanc = sum(metacanc == 1),
    solidtum = sum(solidtum == 1),
    rheumd = sum(rheumd == 1),
    coag = sum(coag == 1),
    obes = sum(obes == 1),
    wloss = sum(wloss == 1),
    fed = sum(fed == 1),
    blane = sum(blane == 1),
    dane = sum(dane == 1),
    alcohol = sum(alcohol == 1),
    drug = sum(drug == 1),
    psycho = sum(psycho == 1),
    depre = sum(depre == 1)
  )

summary_person <-
person_morbidity %>%
  summarise(
    n_people = n_distinct(id),
    n_diagnoses = nrow(smr01_diagnoses),
    chf = sum(chf == 1),
    carit = sum(carit == 1),
    valv = sum(valv == 1),
    pcd = sum(pcd == 1),
    pvd = sum(pvd == 1),
    hypunc = sum(hypunc == 1),
    hypc = sum(hypc == 1),
    para = sum(para == 1),
    ond = sum(ond == 1),
    cpd = sum(cpd == 1),
    diabunc = sum(diabunc == 1),
    diabc = sum(diabc == 1),
    hypothy = sum(hypothy == 1),
    rf = sum(rf == 1),
    ld = sum(ld == 1),
    pud = sum(pud == 1),
    lymph = sum(lymph == 1),
    metacanc = sum(metacanc == 1),
    solidtum = sum(solidtum == 1),
    rheumd = sum(rheumd == 1),
    coag = sum(coag == 1),
    obes = sum(obes == 1),
    wloss = sum(wloss == 1),
    fed = sum(fed == 1),
    blane = sum(blane == 1),
    dane = sum(dane == 1),
    alcohol = sum(alcohol == 1),
    drug = sum(drug == 1),
    psycho = sum(psycho == 1),
    depre = sum(depre == 1)
  )

table_2.1_overall <- add_row(summary_person, summary_admissions) %>%
  write_csv(., "table_2.1_overall.csv")
```

#Functions to count conditions
```{r}

#counts occurence of condition in people
#removes values if less than 5 people
summarise_conditions <-
function(x) {
  x %>%
   summarise(
    n_people = n_distinct(id),
    chf = sum(chf == 1),
    carit = sum(carit == 1),
    valv = sum(valv == 1),
    pcd = sum(pcd == 1),
    pvd = sum(pvd == 1),
    hypunc = sum(hypunc == 1),
    hypc = sum(hypc == 1),
    para = sum(para == 1),
    ond = sum(ond == 1),
    cpd = sum(cpd == 1),
    diabunc = sum(diabunc == 1),
    diabc = sum(diabc == 1),
    hypothy = sum(hypothy == 1),
    rf = sum(rf == 1),
    ld = sum(ld == 1),
    pud = sum(pud == 1),
    lymph = sum(lymph == 1),
    metacanc = sum(metacanc == 1),
    solidtum = sum(solidtum == 1),
    rheumd = sum(rheumd == 1),
    coag = sum(coag == 1),
    obes = sum(obes == 1),
    wloss = sum(wloss == 1),
    fed = sum(fed == 1),
    blane = sum(blane == 1),
    dane = sum(dane == 1),
    alcohol = sum(alcohol == 1),
    drug = sum(drug == 1),
    psycho = sum(psycho == 1),
    depre = sum(depre == 1)
  ) %>%
  mutate_at(vars(chf:depre), function(x) {
    ifelse(x < 5, NA, x)
  })
}

#sums occurence of condition in admissions
#removes values if less than 5 people

summarise_admissions <-
  function(x) {
    x %>%
      summarise(
        n_people = n_distinct(id),
        n_admissions = sum(n_admissions),
        chf = sum(chf),
        carit = sum(carit),
        valv = sum(valv),
        pcd = sum(pcd),
        pvd = sum(pvd),
        hypunc = sum(hypunc),
        hypc = sum(hypc),
        para = sum(para),
        ond = sum(ond),
        cpd = sum(cpd),
        diabunc = sum(diabunc),
        diabc = sum(diabc),
        hypothy = sum(hypothy),
        rf = sum(rf),
        ld = sum(ld),
        pud = sum(pud),
        lymph = sum(lymph),
        metacanc = sum(metacanc),
        solidtum = sum(solidtum),
        rheumd = sum(rheumd),
        coag = sum(coag),
        obes = sum(obes),
        wloss = sum(wloss),
        fed = sum(fed),
        blane = sum(blane),
        dane = sum(dane),
        alcohol = sum(alcohol),
        drug = sum(drug),
        psycho = sum(psycho),
        depre = sum(depre)
      ) %>%
  mutate_at(vars(chf:depre), function(x) {
    ifelse(x < 5, NA, x)
  })
  }
```


#Tables Conditions in People
```{r}
#excludes those with no hospital admissions

demog_morbidity_linked <-
demog_morbidity %>%
  filter(!is.na(chf)) 

demog_morbidity_linked %>%
  group_by(sex) %>%
  summarise_conditions(.) %>%
  write_csv(., "table_2.1_sex.csv")

demog_morbidity_linked %>%
  group_by(age_band) %>%
  summarise_conditions(.) %>%
  write_csv(., "table_2.1_age.csv")

demog_morbidity_linked %>%
  group_by(simd_quintile) %>%
  summarise_conditions(.) %>%
  write_csv(., "table_2.1_deprivation.csv")

shielding_long_morbidity %>%
  filter(!is.na(chf)) %>%
  group_by(shielding_group_description) %>%
  summarise_conditions(.) %>%
  write_csv(., "table_2.1_reasons.csv")
```


#Calculate admissions per person
```{r}
admission_morbidity_person <-
admission_morbidity %>%
      group_by(id) %>%
      summarise(
        n_admissions = n_distinct(date),
        chf = sum(chf),
        carit = sum(carit),
        valv = sum(valv),
        pcd = sum(pcd),
        pvd = sum(pvd),
        hypunc = sum(hypunc),
        hypc = sum(hypc),
        para = sum(para),
        ond = sum(ond),
        cpd = sum(cpd),
        diabunc = sum(diabunc),
        diabc = sum(diabc),
        hypothy = sum(hypothy),
        rf = sum(rf),
        ld = sum(ld),
        pud = sum(pud),
        lymph = sum(lymph),
        metacanc = sum(metacanc),
        solidtum = sum(solidtum),
        rheumd = sum(rheumd),
        coag = sum(coag),
        obes = sum(obes),
        wloss = sum(wloss),
        fed = sum(fed),
        blane = sum(blane),
        dane = sum(dane),
        alcohol = sum(alcohol),
        drug = sum(drug),
        psycho = sum(psycho),
        depre = sum(depre)
      ) %>%
  mutate(id = as.numeric(id))


#add admissions data to demographics table
demog_admissions <-
demog %>%
  left_join(., admission_morbidity_person, by = "id")

#add admissions data to shielding reasons table 
shielding_long_admissions <-
shielding_long %>%
  left_join(., admission_morbidity_person, by = "id")
```

#Tables Admissions
```{r}
#excludes those with no hospital admissions
demog_admissions_linked <-
demog_admissions %>%
  filter(!is.na(n_admissions)) 

demog_admissions_linked %>%
  group_by(sex) %>%
  summarise_admissions(.) %>%
  adorn_totals %>%
  write_csv(., "table_2.1_sex_admissions.csv")

demog_admissions_linked %>%
  group_by(age_band) %>%
  summarise_admissions(.) %>%
  adorn_totals() %>%
  write_csv(., "table_2.1_age_admissions.csv")

shielding_long_admissions %>%
  filter(!is.na(chf)) %>%
  group_by(shielding_group_description) %>%
  summarise_admissions(.) %>%
  write_csv(., "table_2.1_reasons_admissions.csv")
```


#Double counting error summary
```{r}
main_condition_last_admission %>%
  summarise(
    F204 = sum(str_detect(main_condition, "F204")),
    F315 = sum(str_detect(main_condition, "F315")),
    G114 = sum(str_detect(main_condition, "G114")),
    I110 = sum(str_detect(main_condition, "I110")),
    I120 = sum(str_detect(main_condition, "I120")),
    I130 = sum(str_detect(main_condition, "I130")),
    I131 = sum(str_detect(main_condition, "I131")),
    I132 = sum(str_detect(main_condition, "I132")),
    I278 = sum(str_detect(main_condition, "I278")),
    I279 = sum(str_detect(main_condition, "I279")),
    I426 = sum(str_detect(main_condition, "I426")),
    K700 = sum(str_detect(main_condition, "K700")),
    K703 = sum(str_detect(main_condition, "K703")),
    K709 = sum(str_detect(main_condition, "K709"))) %>%
  write_csv(., "appendix_table.csv")
```


#Deprivation Table Admissions
```{r}
demog_admissions_linked %>%
  group_by(simd_quintile) %>%
  summarise_admissions(.) %>%
  adorn_totals %>%
  write_csv(., "table_2.1_simd_admissions.csv")
```





